SDR enhancement by clouds \\\large{A Short Subtitle}

### 2023-11-28 article/article.qmd
Commit 2023-11-28 15:09

Data with quality control

### Data selection

To preserve an unbiased representation of the data we applied a constrain similar the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there must exist at list 45 minutes of valid measurements, including night time near sunrise and sunset. Days with less than 5 valid hours are rejected completely.

<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7), otherwise all data for this day is flagged as invalid. There must be at least This work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid, otherwise all minute data for this hour is flagged as invalid. -->

-   CastillejoCuberos2020
-   valid data 45min /h and 5h / day
-   SZA above biology

Clear sky identification

-   helps on determining thresholds

Criteria for enhancement based on TSI

>>>>

## Data quality control

## Data selection

To preserve an unbiased representation of the data we applied a constrain similar the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there must exist at list 45 minutes of valid measurements, including night time near sunrise and sunset. Days with less than 5 valid hours are rejected completely. <!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7), otherwise all data for this day is flagged as invalid. There must be at least This work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid, otherwise all minute data for this hour is flagged as invalid. --> Furthermore, due to a systematic obstruction of the horizon and the significant measurement uncertainty on large SZAs, we excluded all data with $SZA > `r 90 - BIO_ELEVA`^\circ$.

## Clear sky identification

Use it to find some interesting days to manual check the CE thresholds. No other usage of clear/cloud characterization in CE.

## Criteria for enhancement based on TSI

Many have used models or some statistical method to determine then CE thresholds.

....... cite ...... Descriptions

We used as reference the .... extraterrestrial horizontal irradiance .....

ETH := cosde(SZA) * \text{TSI}

### 2023-11-28 article/article.tex
Commit 2023-11-28 15:09

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Data with quality control

\hypertarget{data-selection}{%
\subsubsection{Data selection}\label{data-selection}}

To preserve an unbiased representation of the data we applied a
constrain similar the one used by \citet{CastillejoCuberos2020}. Where,
for each valid hour of day, there must exist at list 45 minutes of valid
measurements, including night time near sunrise and sunset. Days with
less than 5 valid hours are rejected completely.

\begin{itemize}
\tightlist
\item
  CastillejoCuberos2020
\item
  valid data 45min /h and 5h / day
\item
  SZA above biology
\end{itemize}

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, toptitle=1mm, titlerule=0mm, colbacktitle=quarto-callout-important-color!10!white, rightrule=.15mm, left=2mm, opacityback=0, bottomtitle=1mm, coltitle=black, leftrule=.75mm, breakable, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-important-color-frame, opacitybacktitle=0.6, toprule=.15mm]

>>>>

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced]}{\end{tcolorbox}}\fi

@@

\hypertarget{data-quality-control}{%
\subsection{Data quality control}\label{data-quality-control}}

\hypertarget{data-selection}{%
\subsection{Data selection}\label{data-selection}}

To preserve an unbiased representation of the data we applied a
constrain similar the one used by \citet{CastillejoCuberos2020}. Where,
for each valid hour of day, there must exist at list 45 minutes of valid
measurements, including night time near sunrise and sunset. Days with
less than 5 valid hours are rejected completely. Furthermore, due to a
systematic obstruction of the horizon and the significant measurement
uncertainty on large SZAs, we excluded all data with \(SZA > 78^\circ\).

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, left=2mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, leftrule=.75mm, toprule=.15mm, coltitle=black, titlerule=0mm, arc=.35mm, opacitybacktitle=0.6, bottomtitle=1mm, breakable, colframe=quarto-callout-important-color-frame, opacityback=0, bottomrule=.15mm, colbacktitle=quarto-callout-important-color!10!white, colback=white, toptitle=1mm]
